---
title: "Discretion Mapping"
subtitle: ""
author: "Martin Gleason, MS"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  xaringan::moon_reader:
    css: ["libs/remark-css/default.css", "pro_presentation.css"]
    self_contained: no
    lib_dir: libs
    seal: false
    nature:
      beforeInit: "macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r, packages, include= TRUE, echo = FALSE, message = FALSE, error = FALSE, warning=FALSE}
library("showtext")
library("sysfonts")
library("tidyverse")
library("lubridate")
library("showtext")


font_add_google(name = "Nobile")

source("discretion_word_cloud.R")
```
class: title-slide
class: inverse
class: middle

# Discretion Mapping
.bottom[.right[`r today() %>% format("%A, %B %m, %Y")`]]
---
# What Is Core

* Committee for Results on Equity

--

* From our efforts on Disproportionate Minority Contact


--

* Advises MOAT to ensure policy and program equity regardles of identity, including:

  + Racial
  + Ethnic
  + Gender
  + Sexual
  + Religious
  
---

# The Mapping Project

* Definition of Discretion: 
  + Discretion refers to the choices made by the officer when implementing
    - policy
    - practice
    - or referring to a program. 

* Scope

 + Limited to Probation and Court Services
 
 + Mapping areas of discretion, not measuring discretion
 
 
---
# Method: 
## Three distinction sections

* Pre-trial
  + Detention Screening
  + Expeditor

* Trial/Hearing
  + Adjudication
  + Field
  
* Services
  + Field
  + Clinical
---

# Method: 
## Through the System

* Young man of color traveling through probation
* Data sources
  + Policies
  + Forms
  + Program Documentaion
  + Interviews with DCPOs, SPOs, POs
---

# Exploring our notes
```{r, wordcloud, include = TRUE, message=FALSE, echo =FALSE, error = FALSE, fig.align='center'}

  wordcloud(discretion_words$word, discretion_words$n, min.freq = 5, random.order = FALSE,
            random.color = FALSE, 
            color = pro_colors_scheme2,
            scale = c(3, 1 ))
```
---
Next Step
---
Thank you
