---
title: "Discretion Mapping"
subtitle: ""
author: "Martin Gleason, MS"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  xaringan::moon_reader:
    css: ["libs/remark-css/default.css", "pro_presentation.css"]
    self_contained: no
    lib_dir: libs
    seal: false
    nature:
      beforeInit: "macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
```{r, packages, include= TRUE, echo = FALSE, message = FALSE, error = FALSE, warning=FALSE}
library("showtext")
library("sysfonts")
library("tidyverse")
library("lubridate")
library("showtext")


font_add_google(name = "Nobile")

source("discretion_word_cloud.R")
```
class: title-slide
class: inverse
class: middle

# Discretion Mapping
.bottom[.right[`r today() %>% format("%A, %B %m, %Y")`]]
---
```{r, wordcloud, include = TRUE, message=FALSE, echo =FALSE, error = FALSE, fig.align='center'}

  wordcloud(discretion_words$word, discretion_words$n, min.freq = 5, random.order = FALSE,
            random.color = FALSE, 
            color = pro_colors_scheme2,
            scale = c(3, 1 ))
```
---
# what is core
* Committee for Results on Equity

--
* From our efforts on Disproportionate Minority Contact

--

* Advises MOAT to ensure policy and program equity regardles identity, including:

  + Racial
  + Ethnic
  + Gender
  + Sexual
  + Religious
  
## mapping
* defined 
* scope
 + no assessment or evaluation
---
# Method: Three distinction sections
* pre
  + detention screening
  + expidtior
  
* trial
  + Adjudication
  + Field
  
* supervision
  + Field
  + Clinical
---
—young mN of color traveling through probation
—Data sources
——p&p
——interviews
——review of forms
---
Next Step
---
Thank you
